Variable creation ObjectInAction

### 2020-09-29 Final_Manuscript.Rmd
more cleaning

```{r data}
clark_final <- read.csv("Cleaned data/clark_final.csv")
smith_final <- read.csv("Cleaned data/smith_final.csv")
clarksmith_women <- read.csv("Cleaned data/clarksmith_women.csv")
```

@@

## Analysis Strategy
```{r apim, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Basic actor-partner interdependence model (APIM) depiction."}
include_graphics("APIM_figure.png")
```

@@

## Main Results
```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="This figure depicts the relationships tested bewteen study variables. The light gray variables represent redundant variables and are shown to emphasize the dyadic nature of the data. The estimates were from obtained from separate MLMs. Sample was controlled for in all models. The effects of TSO, actor other-objectification, and partner other-objectification are from a model where the interaction of TSO and partner other-objectification had been trimmed. *p < .05, dashed lines represent non-significant relationships."}
include_graphics("SEMfigure.png")
```

>>>>

```{r data}
clark_final <- read.csv("Cleaned-data/clark_final.csv")
smith_final <- read.csv("Cleaned-data/smith_final.csv")
clarksmith_women <- read.csv("Cleaned-data/clarksmith_women.csv")
```

@@

## Analysis Strategy
```{r apim, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Basic actor-partner interdependence model (APIM) depiction."}
include_graphics("figures/APIM_figure.png")
```

@@

## Main Results
```{r semfigure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="This figure depicts the relationships tested bewteen study variables. The light gray variables represent redundant variables and are shown to emphasize the dyadic nature of the data. The estimates were from obtained from separate MLMs. Sample was controlled for in all models. The effects of TSO, actor other-objectification, and partner other-objectification are from a model where the interaction of TSO and partner other-objectification had been trimmed. *p < .05, dashed lines represent non-significant relationships."}
include_graphics("figrues/SEMfigure.png")
```

### 2020-09-29 Variable creation.Rmd
more cleaning

#Load data
```{r}
#clark
clark_measures <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Measures_1.sav")
clark_pairwise <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Pairwise_1.sav")

#smith
smith <- read_spss("Raw data/Smith College Relationships Data/College_Relationship_Dyadic_September_14_2018_12_17.sav")

clark_sentences <- read.csv("Raw data/Clark College Relationships Data/sexist sentences/coded_sentences.csv")

#trigrams
trigram_check <- read.csv("Raw data/Clark College Relationships Data/trigrams/AMELIA_check_trigram_grading.csv")
```

@@

Step not needed...processing continues
```{r}
#Write out csv with created variables
#write.csv(clark_measures, "Cleaned data/clark_measures.csv")
#write.csv(smith, "Cleaned data/smith.csv")
```

@@

##Write out file to grade
#write.csv(smith_trigrams_long, "Raw data/Smith College Relationships Data/trigrams_to_grade.csv", row.names=FALSE)

#Read in graded trigram file
smith_trigrams_graded <- read.csv("Raw data/Smith College Relationships Data/trigrams_graded.csv")

@@

#Write out csv
#write.csv(smith_sentences_long, "Raw data/Smith College Relationships Data/sexist_sentences_for_coding.csv", row.names = FALSE)

#Read in coded sentences, code correlations
kat_codes <- read.csv("Raw data/Smith College Relationships Data/kat_recode.csv")
xinyu_codes <- read.csv("Raw data/Smith College Relationships Data/xinyu_recode.csv")

@@

Write out cleaned data!
```{r}
write.csv(smith_final, "Cleaned data/smith_final.csv" )
write.csv(clark_final, "Cleaned data/clark_final.csv")
```

>>>>

#Load data
```{r}
#clark
clark_measures <- read_spss("Raw-data/Clark College Relationships Data/College_Relationship_Measures_1.sav")
clark_pairwise <- read_spss("Raw-data/Clark College Relationships Data/College_Relationship_Pairwise_1.sav")

#smith
smith <- read_spss("Raw-data/Smith College Relationships Data/College_Relationship_Dyadic_September_14_2018_12_17.sav")

clark_sentences <- read.csv("Raw-data/Clark College Relationships Data/sexist sentences/coded_sentences.csv")

#trigrams
trigram_check <- read.csv("Raw-data/Clark College Relationships Data/trigrams/AMELIA_check_trigram_grading.csv")
```

@@

Step not needed...processing continues
```{r}
#Write out csv with created variables
#write.csv(clark_measures, "Cleaned-data/clark_measures.csv")
#write.csv(smith, "Cleaned-data/smith.csv")
```

@@

##Write out file to grade
#write.csv(smith_trigrams_long, "Raw-data/Smith College Relationships Data/trigrams_to_grade.csv", row.names=FALSE)

#Read in graded trigram file
smith_trigrams_graded <- read.csv("Raw-data/Smith College Relationships Data/trigrams_graded.csv")

@@

#Write out csv
#write.csv(smith_sentences_long, "Raw-data/Smith College Relationships Data/sexist_sentences_for_coding.csv", row.names = FALSE)

#Read in coded sentences, code correlations
kat_codes <- read.csv("Raw-data/Smith College Relationships Data/kat_recode.csv")
xinyu_codes <- read.csv("Raw-data/Smith College Relationships Data/xinyu_recode.csv")

@@

Write out Cleaned-data!
```{r}
write.csv(smith_final, "Cleaned-data/smith_final.csv" )
write.csv(clark_final, "Cleaned-data/clark_final.csv")
```
